sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-04-04 inst/documents/sensi_an_rotations1.Rmd
add extra outputs

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=4}
#results='hide',

@@

n_scenarios <- 100

@@

for(i in 1:n_scenarios)
{
  # inputs (could also be saved to a dataframe first & extracted one row at a time)
  linputs <- list()
  # constant inputs
  # for Ians Q1 set coverage to 1 & cost to 0 
  linputs$coverage <- 1
  #linputs$migration <- 0.1
  linputs$cost <- 0.1 #0
  linputs$max_gen <- 400
  # variable inputs
  linputs$expo_hi <-  runif(1, min=0.1, max=0.9)
  linputs$eff <-      runif(1, min=0.3, max=1)

  # because I want to compare sequence rot_when_r to rotation
  # I could run all the scenarios above for both seq & rot
  # (and filter out later)

@@

  for(rot_or_not in 0:1)
  {  
    #to get rot_int of 0 every other run
    if (rot_or_not == 0) linputs$rot_interval <- 0

@@

    # summarise results per scenario
    # NOTE this is also currently calc at end of run_rot() prob better to calc there
    # and put in the output dfres, but its then repeated per 
    # TODO first AG fix this maybe go for non dplyr solution
    # if I do calc in run_rot then just find value at first row for each gene
    # Error in dplyr::filter(active_or_refuge == "active") : 
    # object 'active_or_refuge' not found
    res <- dfres %>%
    # only assess in control areas not in refugia  
    dplyr::filter(active_or_refuge=='active') %>%
    group_by(resist_gene) %>%
    # for all insecticides in all generations  
    # summarise(gens_under50 = sum(resistance < 0.5, na.rm=TRUE)) %>%
    # summarise(mean_gens_under50 = mean(gens_under50)) %>%
    # just for deployed insecticides 
    summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                     #finds insecticide in use = this one
                                     resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
                                 summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
                                 unlist()

    #print scenario num and inputs to doc for exploration
    cat("scenario",i,
        " expo_hi",signif(linputs$expo_hi,2),
        " eff",signif(linputs$eff,2),
        " rot_interval",linputs$rot_interval,
        "\n")

    #print results in doc for diagnostics
    cat("tot gens deployed under freq 0.5 =", res,"\n\n")

@@

  } #end rot_or_not loop
} #end scenario loop

@@

>>>>

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)
  library(gridExtra)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=11, comment=NA}
#results='hide',
#comment=NA removes ## before text output

@@

n_scenarios <- 200

@@

for(i in 1:n_scenarios)
{
  # inputs (could also be saved to a dataframe first & extracted one row at a time)
  linputs <- list()

  # for Ians Q1 set coverage to 1 & cost to 0 
  # April 2018, having go at including variable cost, may want to do some cost=0 runs later

  ## constant inputs ##
  linputs$coverage <- 1
  linputs$migration <- 0
  #linputs$cost <- 0 #variable cost below
  linputs$max_gen <- 500

  #beware min_rwr_interval, it's to stop repeated small rotations
  linputs$min_rwr_interval = 5
  #set plot to F if using grid.arrange as in phaps-rotations-better.Rmd
  linputs$plot <-     FALSE

  ## variable inputs ##
  linputs$cost <-           runif(1, min=0,   max=0.1) 
  linputs$expo_hi <-        runif(1, min=0.4, max=0.9)  #min=0.1, max=0.9
  linputs$male_expo_prop <- runif(1, min=0,   max=1)
  linputs$eff <-            runif(1, min=0.5, max=1) # min=0.3, max=1
  linputs$rr  <-            runif(1, min=0.1, max=0.9)
  linputs$dom_sel <-        runif(1, min=0,   max=1)
  linputs$dom_cos <-        runif(1, min=0,   max=1) 
  linputs$start_freqs <-    runif(1, min=0.005,   max=0.1) #note not log yet   
  linputs$n_insecticides <- sample( 2:5, 1 )  #beware set replace=T if more than 1

@@

  # create null objects used plater for plotting
  ggrot <- ggseq <- NULL

  # to compare sequence to rotation run all the scenarios above for both seq & rot 
  # beware has to be 1:0 because interval is overwritten for seq
  for(rot_or_not in 1:0)
  {  
    #to get rot_int of 0 every other run
    if (rot_or_not == 0) linputs$rot_interval <- 0

@@

    # summarise results per scenario
    # NOTE this is also currently calc at end of run_rot() here or other post-process is probably better
    # and put in the output dfres, but the value has to be rpeated for every generation 
    res <- dfres %>%
      # only assess in control areas not in refugia  
      dplyr::filter(active_or_refuge=='active') %>%
      group_by(resist_gene) %>%
      # for all insecticides in all generations  
      # summarise(gens_under50 = sum(resistance < 0.5, na.rm=TRUE)) %>%
      # summarise(mean_gens_under50 = mean(gens_under50)) %>%
      # just for deployed insecticides 
      summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                       #finds insecticide in use = this one
                                       resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
      summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
      unlist()

@@

    ggres <- rot_plot_resistance(dfres, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
    gens_res <- as.numeric(gens_under_thresh(dfres))

    # to plot results for checking
    if ( linputs$rot_interval == 0 )
    {
      ggseq <- ggres
      gens_seq <- gens_res
    } else
    {
      ggrot <- ggres
      gens_rot <- gens_res
    }

  } #end rot_or_not loop

  #printing input values
  #print(unlist(linputs))

  # try to plot input vals instead
  # extract out those between 0 & 1
  dfi <- data.frame(t(as.data.frame(linputs)))
  names(dfi) <- 'value'
  dfi$inputs <- rownames(dfi)

  #take out columns not between 0 & 1
  dfi <- filter(dfi, !inputs %in% c('max_gen','rot_interval','n_insecticides','plot','min_rwr_interval'))
  #also remove coverage & migration both set to 0 for now
  dfi <- filter(dfi, !inputs %in% c('coverage','migration'))

  ggins <- ggplot(dfi, aes(x=inputs,y=value)) + 
            geom_point() +
            theme_minimal() +
            ylim(0,1) +
            theme(axis.text.x = element_text(angle = 20,hjust = 1, vjust = 1))

  grid.arrange(ggrot, ggseq, ggins, ncol=1)

  cat('scenario',i,'sum generations deployed insecticide under thresh rotation:', gens_rot,' sequence:',gens_seq,"\n\n")

  #can I give the code to rerun this scenario
  cat(paste0("run_rot(n_insecticides=",linputs$n_insecticides,", ",
              "cost=",signif(linputs$cost,2),", ",
              "start_freqs=",signif(linputs$start_freqs,2),", ", 
              "rot_interval=",linputs$rot_interval,", ",
              "eff=",signif(linputs$eff,2),",\n",
              "dom_sel=",signif(linputs$dom_sel,2),", ",
              "dom_cos=",signif(linputs$dom_cos,2),", ",
              "rr=",signif(linputs$rr,2),", ",
              "expo_hi=",signif(linputs$expo_hi,2),", ",
              "coverage=",signif(linputs$coverage,2),",\n",
              "migration=",signif(linputs$migration,2),", ",
              "max_gen=",linputs$max_gen,", ", 
              "min_rwr_interval=",linputs$min_rwr_interval,            
              ")\n") )

} #end scenario loop

@@

# check proportion of scenarios not reaching thresholds by max_runs

    nruns_fail <- df_res_all %>% 
                  filter(tot_gens_dep_under50 == linputs$max_gen) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs not reaching thresholds : ', nruns_fail/(2*n_scenarios) ) #2* beacuse eeach scenario run for seq & rot

# plot gens againts exposure and effectiveness
# as a quick test to see if I can set the starting values of these higher

    gg <- ggplot( df_res_all, aes_string(x='eff',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_all, aes_string(x='expo_hi',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_all, aes_string(x='expo_hi*eff*male_expo_prop',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)
